Age-related changes in plant growth and traits

### 2015-05-14 results_best.Rmd
some work on looking at counts - suspect file doesn't "knit" at the moment

words.top.right.logxy <- function (x) {
output <- data.frame(select(glance(x), r.squared, p.value))
output <- round(output,4)
text(10^((0.70*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.95*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("r squared = ",output[1]),adj=0)
text(10^((0.70*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.9*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("p-value = ",output[2]),adj=0)
}

words.top.right.logx <- function (x) {
output <- data.frame(select(glance(x), r.squared, p.value))
output <- round(output,4)
text(10^((0.70*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.95*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("r squared = ",output[1]),adj=0)
text(10^((0.70*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.9*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("p-value = ",output[2]),adj=0)
}

words.top.right <- function (x) {
output <- data.frame(select(glance(x), r.squared, p.value))
output <- round(output,4)
text(((0.70*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.95*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("r squared = ",output[1]),adj=0)
text(((0.70*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.9*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("p-value = ",output[2]),adj=0)
}

words.bottom.right.logxy <- function (x) {
output <- data.frame(select(glance(x), r.squared, p.value))
output <- round(output,4)
text(10^((0.70*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.1*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("r squared = ",output[1]),adj=0)
text(10^((0.70*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.05*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("p-value = ",output[2]),adj=0)
}
```

@@

##Across species patterns of note
###Size versus proportional propagule investment
- Species that are bigger (by weight) invest a lower proportion of their reproduction in propagules  
   1.  This is another way of showing that larger species get less of a return on their investment in reproduction. They have higher accessory costs. 
```{r, echo=FALSE, message=FALSE}
mod <- lm(log(FinalWeight) ~ (log(PerPropagule))+species,data=subset(SummaryInd,PerPropagule>0))
anova(mod)
plot(PerPropagule ~FinalWeight, data=subset(SummaryInd,RA>0&PerPropagule>0),log="xy", col=col.spp[as.factor(species)],pch=16)
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.top.right.logxy(mod)
text(10^((0.70*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.85*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),"includes species effect",adj=0) 
```

- Species that are bigger also invest a lower proportion of their TOTAL surplus energy in propagules (proportion propagules*RA) 
  + This is noisier than looking simply at proportion reproductive allocation to propagules, because of the RA effects - see below
```{r, echo=FALSE, message=FALSE}
mod <- lm(log(FinalWeight) ~ (log(PropAllocation))*species*age,data=subset(SummaryInd,PerPropagule>0))
plot(PropAllocation ~FinalWeight, data=subset(SummaryInd,RA>0&PerPropagule>0),log="xy", col=col.spp[as.factor(species)],pch=16)
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.top.right.logxy(mod)
text(1000,.6e-4,"includes species effect",adj=0)
anova(mod)
```

@@

#getting counts out of Konrad's reproduction data
```{r, echo=FALSE, message=FALSE}
tmp <- BAER_Investment
FD <- as.data.frame(tmp$FD)
BAER_count <- FD %>%
  group_by(Individual, what) %>%
  summarise_each(funs(sum), count, weight)
BAER_count <- subset(BAER_count, count!=0)
BAER_count$species <- "BAER"

>>>>

words.top.right.logxy <- function (x) {
output <- data.frame(select(glance(x), r.squared, p.value))
output <- round(output,4)
text(10^((0.75*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.93*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("r squared = ",output[1]),adj=0,cex=.9)
text(10^((0.75*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.88*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("p-value = ",output[2]),adj=0,cex=.9)
text(10^((0.99*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.98*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),summary(mod)[1],cex=.7,adj=1)
}

words.top.right.logx <- function (x) {
output <- data.frame(select(glance(x), r.squared, p.value))
output <- round(output,4)
text(10^((0.75*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.93*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("r squared = ",output[1]),adj=0,cex=.9)
text(10^((0.75*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.88*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("p-value = ",output[2]),adj=0,cex=.9)
text(10^((0.99*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.98*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),summary(mod)[1],cex=.7,adj=1)
}

words.top.right <- function (x) {
output <- data.frame(select(glance(x), r.squared, p.value))
output <- round(output,4)
text(((0.75*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.93*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("r squared = ",output[1]),adj=0,cex=.9)
text(((0.75*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.88*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("p-value = ",output[2]),adj=0,cex=.9)
text(((0.99*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.98*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),summary(mod)[1],cex=.7,adj=1)
}

words.bottom.right.logxy <- function (x) {
output <- data.frame(select(glance(x), r.squared, p.value))
output <- round(output,4)
text(10^((0.75*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.12*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("r squared = ",output[1]),adj=0,cex=.9)
text(10^((0.75*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.07*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("p-value = ",output[2]),adj=0,cex=.9)
text(10^((0.99*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.02*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),summary(mod)[1],cex=.7,adj=1)
}
```

@@

##Across species patterns of note
###Size versus proportional propagule investment
- Species that are bigger (by weight) invest a lower proportion of their reproduction in propagules  
   1.  This is another way of showing that larger species get less of a return on their investment in reproduction. They have higher accessory costs. 
   - There is also an increase in propagule investment with age
```{r, echo=FALSE, message=FALSE}
mod <- lm(log(FinalWeight) ~ (log(PerPropagule))+age,data=subset(SummaryInd,PerPropagule>0))
summary(mod)
plot(PerPropagule ~FinalWeight, data=subset(SummaryInd,RA>0&PerPropagule>0),log="xy", col=col.spp[as.factor(species)],pch=16)
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.top.right.logxy(mod)
text(10^((0.70*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.85*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),"includes age effect",adj=0) 
```

- Species that are bigger also invest a lower proportion of their TOTAL surplus energy in propagules (proportion propagules*RA) 
  + This is noisier than looking simply at proportion reproductive allocation to propagules, because of the RA effects - see below
```{r, echo=FALSE, message=FALSE}
mod <- lm(log(FinalWeight) ~ (log(PropAllocation))*age,data=subset(SummaryInd,PerPropagule>0))
plot(PropAllocation ~FinalWeight, data=subset(SummaryInd,RA>0&PerPropagule>0),log="xy", col=col.spp[as.factor(species)],pch=16)
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.top.right.logxy(mod)
text(1000,.6e-4,"includes age effect (increase in Prop Allocation with age)",adj=0)
summary(mod)
```

@@

##Looking at 
- Species that are smaller have lower seed set -> this is likely what is causing Propagule allocation to decrease with size
- Also a small increase in seedset with age - but a smaller effect

```{r, echo=FALSE, message=FALSE}
par(mfrow=c(2,2), cex=1, omi=c(.1,0.1,0.1,0.1), mai=c(1.2,1,0.1,0.1))
mod <- lm(log(FinalWeight)~log(seedset),data=subset(SummaryInd,seedset>0))
plot(seedset ~ FinalWeight,data=subset(SummaryInd,seedset>0),
          col=col.spp[as.factor(species)],
          pch=16,log="xy",xlab="",ylab="seed set")
words.bottom.right.logxy(mod)

mod <- lm(log(RA)~log(seedset),data=subset(SummaryInd,seedset>0))
plot(seedset ~ RA,data=subset(SummaryInd,seedset>0),
          col=col.spp[as.factor(species)],
          pch=16,log="xy",ylab="",xlab="")
words.bottom.right.logxy(mod)
mod <- lm(log(FinalWeight)~log(seed_count),data=subset(SummaryInd,seed_count>0))
plot(seed_count ~ FinalWeight,data=subset(SummaryInd,seed_count>0),
          col=col.spp[as.factor(species)],
          pch=16,log="xy",xlab="plant weight",ylab="seed count")
words.bottom.right.logxy(mod)
mod <- lm(log(RA)~log(seed_count),data=subset(SummaryInd,seed_count>0))
plot(seed_count ~ RA,data=subset(SummaryInd,seed_count>0),
          col=col.spp[as.factor(species)],
          pch=16,log="xy",ylab="")
words.bottom.right.logxy(mod)
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
```

```{r, echo=FALSE, message=FALSE}
mod <- lm(log(FinalWeight)~log(PerPropagule),data=subset(SummaryInd,seedset>0))
plot(PerPropagule~FinalWeight,data=subset(SummaryInd,PerPropagule>0),col=col.spp[as.factor(species)],pch=16,log="xy")
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.top.right.logxy(mod)
```

- However, as shown above, there is no clear shift across plant size in pre-pollination allocation   
```{r, echo=FALSE, message=FALSE}
mod <- lm(asin(sqrt(PerPrePol_All)) ~log(FinalWeight)*age, data=subset(SummaryInd,PerPrePol_All>0))
anova(mod)
```

- There is however a decrease in RA with plant size at a given age (across species effect)
```{r, echo=FALSE, message=FALSE}
mod <- lm(asin(sqrt(RA)) ~ log(FinalWeight)*age, data=subset(SummaryInd,RA>0))
plot(asin(sqrt(RA))~FinalWeight,data=subset(SummaryInd,seedset>0),col=col.spp[as.factor(species)],pch=16,log="x")
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.top.right.logx(mod)
anova(mod)
```

- Together this indicates that increased propagule allocation is due to increased seedset, which increases RA in smaller-sized species
```{r, echo=FALSE, message=FALSE}
mod <- lm(asin(sqrt(RA))~age*species,data=subset(SummaryInd,RA>0))
anova(mod)
```

- seedset and Proportional allocation to propagules (vs. all accessory tissues) are well correlated, within and across species  
```{r, echo=FALSE, message=FALSE}
mod <- lm(log(seedset)~log(PerPropagule),data=subset(SummaryInd,seedset>0))
plot(PerPropagule~seedset,data=subset(SummaryInd,seedset>0),col=col.spp[as.factor(species)],pch=16,log="xy")
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)

anova(mod)
```

- however, seedset and seed size are much less well correlated
- so for this collection of species, shifts in accessory costs are closely linked to seed_set
- seed set therefore clearly plays a role in the (small) shifts in RA with plant size
```{r, echo=FALSE, message=FALSE}
mod <- lm(log(seedset)~log(seed_size),data=subset(SummaryInd,seedset>0))

plot(seed_size~seedset,data=subset(SummaryInd,PerPropagule>0),col=col.spp[as.factor(species)],pch=16,log="xy")
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.top.right.logxy(mod)
```

- there is no relationship between seed_count and Final Weight
```{r, echo=FALSE, message=FALSE}
mod <- lm(log(FinalWeight)~log(seed_count),data=subset(SummaryInd,seed_count>0))
plot(seed_count~FinalWeight,data=subset(SummaryInd,seed_count>0),col=col.spp[as.factor(species)],pch=16,log="xy")
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)
```

```{r, echo=FALSE, message=FALSE}
mod <- lm(log(FinalWeight)~log(fruit_weight),data=subset(SummaryInd,fruit_weight>0))
plot(fruit_weight~FinalWeight,data=subset(SummaryInd,fruit_weight>0),col=col.spp[as.factor(species)],pch=16,log="xy")
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)
```

```{r, echo=FALSE, message=FALSE}
mod <- lm(log(ReproInv)~log(fruit_weight),data=subset(SummaryInd,fruit_weight>0))
plot(fruit_weight~ReproInv,data=subset(SummaryInd,fruit_weight>0),col=col.spp[as.factor(species)],pch=16,log="xy")
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)
```

- producing more seeds has a limited effect on RA  
- it is proprtion of flowers/buds that become seeds (seed set) that matters
```{r, echo=FALSE, message=FALSE}
mod <- lm(log(RA)~log(seed_count),data=subset(SummaryInd,seed_count>0))
plot(seed_count~RA,data=subset(SummaryInd,seed_count>0),col=col.spp[as.factor(species)],pch=16,log="xy")
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)

yvar <- "seed_count"
xvar <- "RA"

data <- subset(SummaryInd, seed_count>0)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm((log(x[[yvar]])) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

- However, producing more reproductive units increases RA  - this is a within species effect mostly  
```{r, echo=FALSE, message=FALSE}
mod <- lm(log(RA)~log(repro_count),data=subset(SummaryInd,repro_count>0))
plot(repro_count~RA,data=subset(SummaryInd,repro_count>0),col=col.spp[as.factor(species)],pch=16,log="xy")
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)

yvar <- "repro_count"
xvar <- "RA"

data <- subset(SummaryInd, repro_count>0)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm((log(x[[yvar]])) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

results
```
#getting counts out of Konrad's reproduction data - this code now also appears in "summary_dataframe.R", where it belongs in the end

```{r, echo=FALSE, message=FALSE}
tmp <- BAER_Investment
FD <- as.data.frame(tmp$FD)
BAER_count <- FD %>%
  group_by(Individual, what) %>%
  summarise_each(funs(sum), count, weight)
BAER_count <- subset(BAER_count, count!=0)
BAER_count$species <- "BAER"
